Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-11 paper.tex
principles: address @mblondel's comments

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspectability.]
       \sklearn objects store their constructor parameters
       as well as parameter values determined by learning algorithms
       as public attributes in a documented format.
       (The Python language does not actually distinguish
       between public and private attributes of objects,
       but by convention, any identifier
       prefixed with an underscore (\texttt{\_})
       is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[No proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values,
       are represented as standard Python, NumPy and SciPy classes
       rather than custom ones whenever feasible.
       Custom classes adhere to Python conventions and protocols
       for constructs such as iteration over the ``folds''
       in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composability.]
       Many machine learning tasks are expressible
       as \textit{pipelines} of transformations to data.
       Other tasks are naturally viewed
       as modifications to other tasks;
       e.g., multi-label classification
       can be reduced to multiple binary classification tasks.
       Accordingly, multi-label classification
       is implemented by a class that takes an existing classifier object
       as input and modifies its function.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default value for that parameter must be defined by the library
       if at all possible,
       and the default should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

The API is designed to adhere to the following broad principles:
\begin{description}
  \item[Inspectability.]
       \sklearn objects store their constructor parameters
       as well as parameter values determined by learning algorithms
       as public attributes in a documented format.
       (The Python language does not actually distinguish
       between public and private attributes of objects,
       but by convention, any identifier
       prefixed with an underscore (\texttt{\_})
       is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Learning algorithms are objects of custom classes,
       but datasets and hyperparameter names and values,
       are represented as standard Python, NumPy and SciPy classes
       rather than custom ones whenever feasible.
       Custom classes adhere to Python conventions and protocols
       for constructs such as iteration over the ``folds''
       in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composability.]
       Many machine learning tasks are expressible
       as \textit{pipelines} of transformations to data.
       Also, some learning algorithms are naturally viewed
       as meta-algorithms parameterized on other algorithms.
       To be able to implement and use these algorithms in a simple way,
       all learners are usable with a consistent set of methods
       and a simple syntax is implemented
       for setting/retrieving parameters of ``sub-estimators''.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default value for that parameter must be defined by the library
       if at all possible,
       and the default should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
